---
title: "Food-labeling.-An-experiment-to-assess-consumer-choices_interactions 29112024 Update d-prime"
author: "Constanza Avalos"
date: "2024-11-29"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
  pdf_document:
    latex_engine: xelatex
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Clear cache

```{r cache}

# Clear the R package cache by removing the temporary directory
unlink(tempdir(), recursive = TRUE)

# Optionally, clear the .Rhistory file if needed
if (file.exists(".Rhistory")) {
  file.remove(".Rhistory")
}

# Clear the workspace
rm(list = ls())

```
## Directory

```{r directory}

# Set a new temporary directory for R
new_temp_dir <- "C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper  1"
dir.create(new_temp_dir, recursive = TRUE, showWarnings = FALSE)
tempdir <- new_temp_dir
Sys.setenv(TMPDIR = new_temp_dir)

# Verify the new temporary directory
print(tempdir)

```

## Import data

The aim of the research is to determine the extent to which the presence or absence of different food labelling affects consumers' decision-making. This is addressed through an online survey, in which data will be collected from each participant. Experimental data collected in August 2024.

Participants chose breakfast cereals in an online shopping experience. This choice task is unique in that each participant is randomly assigned to a group where different types of food labels or none at all will appear. Participants also completed questions about personal and household circumstances to determine how labelling influences choices.

The project has been reviewed by The University of Manchester Research Ethics Committee and approval has been granted to conduct this study (Reference number: 2024-16718-35972). School of Social Sciences Fieldwork Bursary, University of Manchester (Reference number: SF2324/298); and ANID-Chile (Agencia Nacional de Investigación y Desarrollo).

```{r data}

library(readr)
library(dplyr)
library(Matrix)
library(lme4)
library(texreg)

#df <- read_csv("C:/Users/const/OneDrive/Desktop/PhD/Papers and Reports/Paper 1st/4. Dataset/Food labelling WM_03112024.csv")

df <- read_csv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper  1/Food labelling WM_03112024.csv")

#changing column names
colnames(df)[c(146, 156, 161, 166, 98, 136, 141, 103, 104, 105, 106, 107, 108, 109, 110, 27, 32, 185, 126, 131, 125, 119, 120, 93)] <- c("Sex", "Ethnicity", "Level_Education", "Income", "FamiliarityBrands", "Check_Ingredients", "Check_nutricontent", "Cereal healthiness1", "Cereal healthiness2", "Cereal healthiness3", "Cereal healthiness4","Cereal healthiness5","Cereal healthiness6","Cereal healthiness7", "Cereal healthiness8", "Purchase12months", "Consent", "Rtime", "Children", "Responsable", "Loseweight", "Weight", "Height", "Having information")


 df <- df %>%
  mutate(Groups = case_when(
    Groups == "No label" ~ "Absent",
    TRUE ~ as.character(Groups)
  ))

 
```

## Database cleaning, caution: I would not choose\nany of them means

Each participant is assigned to one of three experimental conditions: absent, coarse labels (4 partitions), and detailed labels (8 partitions). In the choice task, one group presents a cereal package with no labels, while two groups present different labels indicating the amount of calories per 100 grams. The task consists of 16 trials.

For each group, the cereal brand is identified with a code in the database. Each cereal brand represents a specific amount of calories per 100 grams. 

Nestle Shredded Wheat Cereal = 360
Quaker Rolled Oats Porridge 500g = 374
Kellogg's Crunchy Nut Breakfast Cereal = 392
Kellogg's Choco Wheats Cereal 480g = 398
Quaker Oat Granola Honey & Almond Cereal = 423
Kellogg's Crunchy Nut Not So Nutty Red Berries Granola = 431
Nestle Curiously Cinnamon Cereal 375g = 453
Kellogg's Krave Chocolate Hazelnut Breakfast Cereal = 470

There was a mistake calculating the calorie count because the alternative I would not choose\nany of them means. It depends on the data set, if it is csv I would not choose any of them.then. 


```{r data2}

library(dplyr)

df <- df %>%
  mutate_at(vars(35:50), 
            funs(case_when(
              . == "IM_e9a6CSGHqHCBcdU" ~ "360",
              . == "IM_cUa2Sgw1Z4KERE2" ~ "374",
              . == "IM_882CtF42zwvUZv0" ~ "392",
              . == "IM_8GNIM0Fzob6BZJQ" ~ "398",
              . == "IM_3r4Nrp3TqC6BOlg" ~ "423",
              . == "IM_6nGGAjM99GrIGwK" ~ "431",
              . == "IM_dgaZUlSdxdpoDbM" ~ "453",
              . == "IM_6DzLXmUBf30NEXA" ~ "470",
              . == "I would not choose any of them." ~ "0",
              TRUE ~ .
            )))

#Without label - Number of calories per trial 

df[,35:50] <- lapply(df[,35:50], as.numeric) #set as numeric variable
which(colnames(df) == "If these were your only breakfast cereal options, which one would you choose to buy?...50") #Number of columns

df <- df %>%
  mutate_at(vars(53:68), 
            funs(case_when(
              . == "IM_1KZpRUO6kugeBJs" ~ "360",
              . == "IM_5uvozsuUyMi5oiO" ~ "374",
              . == "IM_26uPBkRfbvYlNtA" ~ "392",
              . == "IM_87CKtqLPlGEpKyW" ~ "398",
              . == "IM_9GG0vzD8syY5gZ8" ~ "423",
              . == "IM_cDchasU2JMCLGPY" ~ "431",
              . == "IM_bClay6uLEv1947Y" ~ "453",
              . == "IM_38z9sbBLDw2DZye" ~ "470",
              . == "I would not choose\nany of them." ~ "0",
              TRUE ~ .
            )))

#Coarse label - Number of calories per trial 

df[,53:68] <- lapply(df[,53:68], as.numeric) #set as numeric variable
which(colnames(df) == "If these were your only breakfast cereal options, which one would you choose to buy?...68") #Number of column

#Detailed labels

df[df == 'IM_bD60xtkWv7LAzWu'] <- '360'
df[df == 'IM_cvHHTjxvJJQ9Sei'] <- '374'
df[df == 'IM_7UlNvrv1Fpncje6'] <- '392'
df[df == 'IM_3DdXt6qErfzF0HQ'] <- '398'
df[df == 'IM_da6wfDAIiOzWtCu'] <- '423'
df[df == 'IM_cCQp6UJg0Ly2YSO'] <- '423'
df[df == 'IM_0cTjPIwPK25YKai'] <- '431'
df[df == 'IM_8e2MDrjUVIOJZci'] <- '453'
df[df == 'IM_bQ2lxJbuEZc3fpk'] <- '470'
df[df == 'I would not choose\nany of them.'] <- '0'

#Detailed label - Number of calories per trial 

df[,72:87] <- lapply(df[,72:87], as.numeric) #set as numeric variable
which(colnames(df) == "If these were your only breakfast cereal options, which one would you choose to buy?...87") #Number of column

```
## Recoded variables


```{r data3}

library(dplyr)

df$Ethnicity_reco <- ifelse(df$Ethnicity == 'White', "White",
                            ifelse(df$Ethnicity == 'Prefer not to say', "Prefer not to say", "Mixed"))
cross_tab <- table(df$Ethnicity_reco, df$Groups)
print(cross_tab)

df$Income2 <- ifelse(df$Income %in% c("Above £40,000", "£30,001 - £40,000"), "£30,001 - Above £40,000",
                     ifelse(df$Income == "Prefer not to say", "Prefer not to say", "Below £10,000 - £30,000"))
cross_tab1 <- table(df$Income2, df$Groups)
print(cross_tab1)

df$Age2 <- ifelse(df$Age %in% c("18-24", "25-34"), "18-34",
                     ifelse(df$Age %in% c("35-44", "45-54"), "35-54", "55-65+"))
cross_tab2 <- table(df$Age2, df$Groups)
print(cross_tab2)

df$Level_Education2 <- ifelse(df$Level_Education %in% c("Higher or secondary or further education (A-levels, BTEC, etc.)", "Post-graduate degree"), "High Education",
                     ifelse(df$Level_Education == "Prefer not to say", "Prefer not to say", "Low Education"))

df$Groups <- as.factor(df$Groups)
df$Groups <- relevel(df$Groups, ref = 'Absent')
table(df$Groups)

df$Level_Education2 <- as.factor(df$Level_Education2)
df$Level_Education2 <- relevel(df$Level_Education2 , ref = 'Prefer not to say')

df$Loseweight <- as.factor(df$Loseweight)
df$Loseweight <- relevel(df$Loseweight , ref = 'Prefer not to say')

 df <- df %>%  
   # Convert height to meters in a new column  
   mutate(Height_m = Height / 100,  
          BMI = Weight / (Height_m^2)) %>%  
   mutate(BMI_category = case_when(  
     BMI < 18.5 ~ "Underweight",  
     BMI >= 18.5 & BMI < 25 ~ "Normal weight",  
     BMI >= 25 & BMI < 30 ~ "Overweight",  
     BMI >= 30 ~ "Obesity",  
     TRUE ~ NA_character_  
   )) %>%  
   mutate(BMI_category = factor(BMI_category,   
                                levels = c("Underweight", "Normal weight", "Overweight", "Obesity"),  
                                ordered = TRUE)) 
 
cross_tab3 <- table(df$BMI_category, df$Groups)
print(cross_tab3)

cross_tab_percentbmi <- prop.table(cross_tab3, margin = 2) * 100
print(cross_tab_percentbmi)

 
```
## Chi squares comparisons


```{r chi}

 # Create a contingency table of Groups vs. BMI_category  
 bmi_table <- with(df, table(Groups, BMI_category))  
 print(bmi_table)  
   
 # Run the chi-square test  
 chi_test <- chisq.test(bmi_table)  
 print(chi_test)
 
 bmi_table1 <- with(df, table(Groups, Sex)) 
 chi_test1 <- chisq.test(bmi_table1)  
 print(chi_test1)
 
 bmi_table2 <- with(df, table(Groups, Age2)) 
 chi_test2 <- chisq.test(bmi_table2)  
 print(chi_test2)

 bmi_table3 <- with(df, table(Groups, Ethnicity_reco)) 
 chi_test3 <- chisq.test(bmi_table3)  
 print(chi_test3)
 
 bmi_table4 <- with(df, table(Groups, df$Level_Education2)) 
 chi_test4 <- chisq.test(bmi_table4)  
 print(chi_test4)
 
 bmi_table5 <- with(df, table(Groups, df$Income2)) 
 chi_test5 <- chisq.test(bmi_table5)  
 print(chi_test5)

 bmi_table6 <- with(df, table(Groups, df$Children)) 
 chi_test6 <- chisq.test(bmi_table6)  
 print(chi_test6)

 bmi_table7 <- with(df, table(Groups, df$Loseweight)) 
 chi_test7 <- chisq.test(bmi_table7)  
 print(chi_test7)

  bmi_table8 <- with(df, table(Groups, df$Responsable)) 
 chi_test8 <- chisq.test(bmi_table8)  
 print(chi_test8)
 
 bmi_table9 <- with(df, table(Groups, df$Check_Ingredients)) 
 chi_test9 <- chisq.test(bmi_table9)  
 print(chi_test9)
 
 bmi_table10 <- with(df, table(Groups, df$FamiliarityBrands)) 
 chi_test10 <- chisq.test(bmi_table10)  
 print(chi_test10)
 

 df$seeing_labels_combined <- df[[69]]  # First, copy all values from first column
df$seeing_labels_combined[is.na(df$seeing_labels_combined)] <- df[[88]][is.na(df$seeing_labels_combined)]  # Then fill in from second column only where first column is NA

# Subset to only Coarse and Detailed groups, and exclude NA in the combined label variable
subset_df_seeinglabels <- df[df$Groups %in% c("Coarse", "Detailed") & !is.na(df$seeing_labels_combined), ]

table(df$seeing_labels_combined, df$Groups)
table(subset_df_seeinglabels$seeing_labels_combined, subset_df_seeinglabels$Groups)

bmi_table11 <- with(subset_df_seeinglabels, table(Groups, subset_df_seeinglabels$seeing_labels_combined)) 
chi_test11 <- chisq.test(bmi_table11)  
print(chi_test11)

df$Having_information_recode <- as.character(df$`Having information`)
df$Having_information_recode[df$Having_information_recode == 'Information overload' | df$Having_information_recode == 'Somewhat sufficient'] <- 'Overload or Sufficient'

table(df$Having_information_recode, df$Groups)

bmi_table12 <- with(df, table(Groups, Having_information_recode)) 
 chi_test12 <- chisq.test(bmi_table12)  
 print(chi_test12)
 

```
## ANOVA comparisons

ANOVA (Analysis of Variance) rather than t-test. ANOVA is specifically designed for comparing means across three or more groups, while t-tests are limited to comparing two groups at a time.

The p-value (Pr(>F)) is 0.43, which is greater than the conventional significance level of 0.05.
This means there is no statistically significant difference in the mean product preference rankings across your three groups (absent, coarse label, and detailed label).


```{r anova}

anova <- aov(df$`Cereal healthiness1` ~ Groups, data = df)
summary(anova)

anova1 <- aov(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_cUa2Sgw1Z4KERE2` ~ Groups, data = df)
summary(anova1)

anova2 <- aov(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_lnH5RoeqxamC6re` ~ Groups, data = df)
summary(anova2)

anova3 <- aov(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_882CtF42zwvUZv0` ~ Groups, data = df)
summary(anova3)

anova4 <- aov(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_dgaZUlSdxdpoDbM` ~ Groups, data = df)
summary(anova4)

anova5 <- aov(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_3r4Nrp3TqC6BOlg` ~ Groups, data = df)
summary(anova5)

anova6 <- aov(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_6DzLXmUBf30NEXA` ~ Groups, data = df)
summary(anova6)

anova8 <- aov(df$`Cereal healthiness8` ~ Groups, data = df)
summary(anova8)

# Replace Product2, Product5, Product6 with your actual column names  
manova_result <- manova(cbind(`Cereal healthiness1`, `Cereal healthiness2`, `Cereal healthiness3`,`Cereal healthiness4`,`Cereal healthiness5`,`Cereal healthiness6`,`Cereal healthiness7`, `Cereal healthiness8`) ~ Groups, data = df) 
summary(manova_result)

# Post hoc analysis  
 product4_aov <- aov(`Cereal healthiness4` ~ Groups, data = df)  
 TukeyHSD(product4_aov)
 
 product6_aov <- aov(`Cereal healthiness6` ~ Groups, data = df)  
 TukeyHSD(product6_aov)
 
 product8_aov <- aov(`Cereal healthiness8` ~ Groups, data = df)  
 TukeyHSD(product8_aov)



```


## Getting variable 'Calorie Count'

We study how to estimate the effect of an food label format on an outcome using RCTs. This parameter is generally called the Average Treatment Effect (ATE).

The coefficients in the regression output will represent:

Yi = β0 + β1FoodLabels + γXi + ϵi

Where: 

β0 is the mean outcome in the control (absent) group,
β1 is the ATE of Food labels
Xi represents the covariates,
γ represents the coefficients for covariates.

Interpretations of coefficients:

The ATE for 'coarse' labels compared to 'absent' (control group),
The ATE for 'detailed' labels compared to 'absent' (control group)

Model 1, 2, 3, 4, 5, controls by covariates

```{r calories, echo=FALSE}

#Create new variable for number of calories per individual

df$CaloriesNL <- rowMeans(df[, c(35:50)], na.rm = TRUE)
df$CaloriesCo <- rowMeans(df[, c(53:68)], na.rm = TRUE)
df$CaloriesDe <- rowMeans(df[, c(72:87)], na.rm = TRUE)
df$CalorieTotal <- rowSums(df[, c(200:202)], na.rm = TRUE)

mean(df$CaloriesNL, na.rm = TRUE)
mean(df$CaloriesCo, na.rm = TRUE)
mean(df$CaloriesDe, na.rm = TRUE)
mean(df$CalorieTotal)

#library(readr)

#write_csv(df, "C:\\Users\\cavalos\\OneDrive - The Alan Turing Institute\\Desktop\\PhD CAV\\Paper  1\\df.csv")


```

## Getting working memory test Z values 

- The basic formula for a sample is:

z = (x – μ) / σ

For example, let’s say you have a test score of 190. The test has a mean (μ) of 150 and a standard deviation (σ) of 25. Assuming a normal distribution, your score would be:

z = (x – μ) / 

= (190 – 150) / 25 = 1.6.

It is a combination but Participants who achieved less than 6 hits or had more than 17 false alarm in 1-back block do not proceed to 2-back block. 

```{r wm, echo=FALSE}

library(dplyr)
library(ggplot2)
library(tidyr)

# Define our helper functions
safe_qnorm <- function(p) {
  if (is.na(p)) {
    return(NA)
  } else {
    return(qnorm(p))
  }
}

improved_apply_correction <- function(hit_rate, fa_rate, signal_trials, noise_trials) {  
   # Initialize with the original values  
   corrected_hit_rate <- hit_rate  
   corrected_fa_rate <- fa_rate  
     
   # Only apply corrections if values are not NA  
   if (!is.na(hit_rate)) {  
     if (hit_rate == 1) {  
       corrected_hit_rate <- (signal_trials - 0.5) / signal_trials  
     } else if (hit_rate == 0) {  
       corrected_hit_rate <- 0.5 / signal_trials  
     }  
   }  
     
   if (!is.na(fa_rate)) {  
     if (fa_rate == 0) {  
       corrected_fa_rate <- 0.5 / noise_trials 
     } else if (fa_rate == 1) {  
       corrected_fa_rate <- (noise_trials - 0.5) / noise_trials  
     }  
   }  
     
   return(list(hit_rate = corrected_hit_rate, fa_rate = corrected_fa_rate))  
 }  

# Define trial counts
signal_trials <- 30
noise_trials <- 48

# PART 1: Calculate hit rates and false alarm rates for 1-back
df <- df %>%
  mutate(
    hit1 = signal_trials - nBack1MISS,
    hit_rate_1 = hit1 / signal_trials,
    fa_rate_1 = nBack1FA / noise_trials
  )

# PART 2: Apply corrections to 1-back data
df <- df %>%
  rowwise() %>%
  mutate(
    # Apply correction safely
    corrected_1 = list(improved_apply_correction(hit_rate_1, fa_rate_1, signal_trials, noise_trials)),
    corrected_hit_rate_1 = corrected_1$hit_rate,
    corrected_fa_rate_1 = corrected_1$fa_rate
  )
# PART 3: Calculate z-scores for 1-back data using the corrected rates
df <- df %>%
  rowwise() %>%
  mutate(
    z_hit_1 = safe_qnorm(corrected_hit_rate_1),
    z_fa_1 = safe_qnorm(corrected_fa_rate_1),
    dprime1 = if_else(!is.na(z_hit_1) & !is.na(z_fa_1), z_hit_1 - z_fa_1, NA_real_)
  ) %>%
  ungroup()

##### 2-black block

# PART 1: Calculate hit rates and false alarm rates for 1-back
df <- df %>%
  mutate(
    hit2 = signal_trials - nBack2MISS,
    hit_rate_2 = hit2 / signal_trials,
    fa_rate_2 = nBack2FA / noise_trials
  )

# PART 2: Apply corrections to 1-back data
df <- df %>%
  rowwise() %>%
  mutate(
    # Apply correction safely
    corrected_2 = list(improved_apply_correction(hit_rate_2, fa_rate_2, signal_trials, noise_trials)),
    corrected_hit_rate_2 = corrected_2$hit_rate,
    corrected_fa_rate_2 = corrected_2$fa_rate
  )
# PART 3: Calculate z-scores for 1-back data using the corrected rates
df <- df %>%
  rowwise() %>%
  mutate(
    z_hit_2 = safe_qnorm(corrected_hit_rate_2),
    z_fa_2 = safe_qnorm(corrected_fa_rate_2),
    dprime2 = if_else(!is.na(z_hit_2) & !is.na(z_fa_2), z_hit_2 - z_fa_2, NA_real_)
  ) %>%
  ungroup()

##### 3-black block

# PART 1: Calculate hit rates and false alarm rates for 1-back
df <- df %>%
  mutate(
    hit3 = signal_trials - nBack3MISS,
    hit_rate_3 = hit3 / signal_trials,
    fa_rate_3 = nBack3FA / noise_trials
  )

# PART 2: Apply corrections to 1-back data
df <- df %>%
  rowwise() %>%
  mutate(
    # Apply correction safely
    corrected_3 = list(improved_apply_correction(hit_rate_3, fa_rate_3, signal_trials, noise_trials)),
    corrected_hit_rate_3 = corrected_3$hit_rate,
    corrected_fa_rate_3 = corrected_3$fa_rate
  )
# PART 3: Calculate z-scores for 1-back data using the corrected rates
df <- df %>%
  rowwise() %>%
  mutate(
    z_hit_3 = safe_qnorm(corrected_hit_rate_3),
    z_fa_3 = safe_qnorm(corrected_fa_rate_3),
    dprime3 = if_else(!is.na(z_hit_3) & !is.na(z_fa_3), z_hit_3 - z_fa_3, NA_real_)
  ) %>%
  ungroup()


sum(!is.na(df$dprime1))  
sum(!is.na(df$dprime2))  
sum(!is.na(df$dprime3))  
mean(df$dprime2, na.rm = TRUE)
mean(df$dprime3, na.rm = TRUE)
mean(df$dprime1, na.rm = TRUE)
sd(df$dprime1, na.rm = TRUE)
sd(df$dprime2, na.rm = TRUE)
sd(df$dprime3, na.rm = TRUE)

summary_dprime1 <- aggregate(df$dprime1 ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))
summary_dprime2 <- aggregate(df$dprime2 ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))
summary_dprime3 <- aggregate(df$dprime3 ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

# Create a copy of the dataframe  
 df <- df  
   
 # Convert columns that are lists to a collapsed string representation  
 for (col in names(df)) {  
   if (is.list(df[[col]])) {  
     df[[col]] <- sapply(df[[col]], function(x) paste(x, collapse = "; "))  
   }  
 }  
   
 # Write the fixed dataframe to CSV  
 write.csv(df, "df.csv", row.names = FALSE)  
 
```

## ANOVA comparisons N-back

ANOVA (Analysis of Variance) rather than t-test. ANOVA is specifically designed for comparing means across three or more groups, while t-tests are limited to comparing two groups at a time.

The p-value (Pr(>F)) is 0.43, which is greater than the conventional significance level of 0.05.
This means there is no statistically significant difference in the mean product preference rankings across your three groups (absent, coarse label, and detailed label).


```{r anova2}

 ##### N-back
 
anova_dprime1 <- aov(dprime1 ~ Groups, data = df)
summary(anova_dprime1)

anova_dprime2 <- aov(dprime2 ~ Groups, data = df)
summary(anova_dprime2)

anova_dprime3 <- aov(dprime3 ~ Groups, data = df)
summary(anova_dprime3)

```

## Getting working memory test plots

```{r wmplot, echo=FALSE}


# Reshape the dataframe for plotting distributions using tidyr:
plot_data_d <- df %>%
  select(dprime1, dprime2, dprime3) %>%
  pivot_longer(everything(), names_to = "Condition", values_to = "dprime")

# Create the distribution plot using ggplot2:
p <- ggplot(plot_data_d, aes(x = dprime, fill = Condition)) + 
  geom_histogram(bins = 30, alpha = 0.6, position = "identity") +
  facet_wrap(~ Condition, scales = "free") +
  theme_minimal() +
  labs(title = "Z value distribution of d' for Each n-back Level",
       x = "d'",
       y = "Count")

print(p)

# Select columns for FA and MISS for each level:
# nBack1, nBack2, and nBack3
fa_miss_data <- df %>%
  select(nBack1FA, nBack1MISS, nBack2FA, nBack2MISS, nBack3FA, nBack3MISS)

# Reshape the data using gather() for a long format
plot_data1 <- fa_miss_data %>% 
  gather(key = "Measure", value = "Count",
         nBack1FA, nBack1MISS, nBack2FA, nBack2MISS, nBack3FA, nBack3MISS)

# Optionally, create new columns for Condition and Measure, if your column names are formatted
# as e.g. "nBack1FA" where the number and "FA"/"MISS" can be separated.
plot_data2 <- plot_data1 %>%
  mutate(
    Condition = sub("nBack([0-9]).*", "nBack\\1", Measure),
    MeasureType = ifelse(grepl("FA", Measure), "False Alarm", "Miss")
  )

# Create the plot
p1 <- ggplot(plot_data2, aes(x = Count, fill = MeasureType)) +
  geom_histogram(bins = 30, alpha = 0.6, position = "identity") +
  facet_grid(MeasureType ~ Condition, scales = "free") +
  theme_minimal() +
  labs(title = "Distribution of False Alarms and Misses for Each n-back Level",
       x = "Count",
       y = "Frequency")

print(p1)



```

## Getting working memory test plots by treatment groups

```{r wmplot1, echo=FALSE}

long_df <- df %>%  
   select(Groups, dprime1, dprime2, dprime3) %>%  
   gather(key = "Condition", value = "dprime", dprime1, dprime2, dprime3)  
   
 # Adjust the condition names using recode() with string literals  
 long_df <- long_df %>%  
   mutate(Condition = recode(Condition,  
                             "dprime1" = "1-back",  
                             "dprime2" = "2-back",  
                             "dprime3" = "3-back")) 

# Now, calculate mean dprime for each Treatment and Condition combination
summ_df <- long_df %>%
  group_by(Groups, Condition) %>%
  summarise(mean_dprime = mean(dprime, na.rm = TRUE),
            se_dprime = sd(dprime, na.rm = TRUE)/sqrt(n()),
            .groups = "drop")

#Create the boxplot
p_box <- ggplot(long_df, aes(x = Groups, y = dprime, fill = Groups)) +
  geom_boxplot() +
  facet_wrap(~ Condition) +
  scale_fill_manual(values = c("1-back" = "#666666", 
                               "2-back" = "#999999", 
                               "3-back" = "black")) +
  labs(title = "",
       x = "",
       y = "d' score") +
  theme(
    text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman", size = 16, face = "bold"),
    axis.title = element_text(family = "Times New Roman", size = 12),
    axis.text = element_text(family = "Times New Roman", size = 10)
  )

print(p_box)


p_box1 <- ggplot(long_df, aes(x = Groups, y = dprime, fill = Condition)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  labs(title = "Boxplot of d' by Treatment Group",
       x = "Treatment Group",
       y = "d'") +
  theme_minimal()

print(p_box1)

long_df_errors <- df %>%
  select(Groups, 
         nBack1FA, nBack2FA, nBack3FA,
         nBack1MISS, nBack2MISS, nBack3MISS) %>%
  gather(key = "Measure", value = "Count", -Groups) %>%
  mutate(
    Type = ifelse(grepl("FA", Measure), "False Alarm", "Miss"),
    Level = case_when(
      grepl("1", Measure) ~ "1-back n = 498",
      grepl("2", Measure) ~ "2-back n = 464",
      grepl("3", Measure) ~ "3-back n = 452"
    )
  )

# Create boxplot for FA and Misses
p_errors <- ggplot(long_df_errors, aes(x = Level, y = Count, fill = Type)) +
  geom_boxplot() +
  facet_wrap(~Groups) +
  theme_minimal() +
  labs(title = "Distribution of False Alarms and Misses by Treatment",
       x = "n-back Level",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(p_errors)

total_target <- 30  # As defined earlier

long_df_errors_hits <- df %>%
  select(Groups, 
         nBack1FA, nBack2FA, nBack3FA,
         nBack1MISS, nBack2MISS, nBack3MISS) %>%
  # First calculate hits for each level
  mutate(
    nBack1HIT = total_target - nBack1MISS,
    nBack2HIT = total_target - nBack2MISS,
    nBack3HIT = total_target - nBack3MISS
  ) %>%
  # Gather all measures
  gather(key = "Measure", value = "Count", 
         -Groups) %>%
  mutate(
    Type = case_when(
      grepl("FA", Measure) ~ "False Alarm",
      grepl("MISS", Measure) ~ "Miss",
      grepl("HIT", Measure) ~ "Hit"
    ),
    Level = case_when(
      grepl("1", Measure) ~ "1-back",
      grepl("2", Measure) ~ "2-back",
      grepl("3", Measure) ~ "3-back"
    )
  )

# Create boxplot including Hits
p_errors_hits <- ggplot(long_df_errors_hits, aes(x = Level, y = Count, fill = Type)) +
  geom_boxplot() +
  facet_wrap(~Groups) +
  theme_minimal() +
  scale_fill_manual(values = c("False Alarm" = "red", "Miss" = "blue", "Hit" = "green")) +
  labs(title = "Distribution of Hits, False Alarms, and Misses by Treatment",
       x = "n-back Level",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(p_errors_hits)

# Calculate summary statistics including hits
summary_stats_with_hits <- long_df_errors_hits %>%
  group_by(Groups, Level, Type) %>%
  summarise(
    Mean = mean(Count, na.rm = TRUE),
    SD = sd(Count, na.rm = TRUE),
    Median = median(Count, na.rm = TRUE),
    .groups = 'drop'
  )

print(summary_stats_with_hits)


long_df <- df %>%
  select(Groups, 
         nBack1FA, nBack2FA, nBack3FA,
         nBack1MISS, nBack2MISS, nBack3MISS) %>%
  # Calculate hits for each level
  mutate(
    nBack1HIT = total_target - nBack1MISS,
    nBack2HIT = total_target - nBack2MISS,
    nBack3HIT = total_target - nBack3MISS
  ) %>%
  # Gather all response measures into long format
  gather(key = "MeasureDetail", value = "Count", -Groups) %>%
  mutate(
    # Determine the response type (Hit, False Alarm, or Miss)
    Measure = case_when(
      grepl("FA", MeasureDetail) ~ "False Alarm",
      grepl("MISS", MeasureDetail) ~ "Miss",
      grepl("HIT", MeasureDetail) ~ "Hit"
    ),
    # Determine the n-back level
    Level = case_when(
      grepl("1", MeasureDetail) ~ "1-back n = 498",
      grepl("2", MeasureDetail) ~ "2-back n = 464",
      grepl("3", MeasureDetail) ~ "3-back n = 452"
    )
  )

p <- ggplot(long_df, aes(x = Groups, y = Count, fill = Measure)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  facet_wrap(~ Level, nrow = 1) +
  scale_fill_manual(values = c("Hit" = "#666666", 
                               "False Alarm" = "#999999", 
                               "Miss" = "#CCCCCC")) +
  labs(title = "",
       x = "",
       y = "Number of responses") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    legend.title = element_blank(),
    strip.text = element_text(face = "bold")
  )

print(p)

# Export plot as PDF file for high-quality vector graphics
ggsave(filename = "response_patterns_figure.pdf", plot = p, width = 10, height = 6, device = cairo_pdf)


```

## OLS - ATE, average number of calories + Working memory test as an interaction term 

The working memory test consists of three blocks (1-, 2-, and 3-back) of 90 trials each. Participants complete three blocks of 30 trials each of 1- and 2-back sequences, without a sound to signify a correct response.

Relevel categories in R: https://www.youtube.com/watch?app=desktop&v=XJw6xdBYG7c&t=61s

Stargazer: https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf

```{r int, echo=FALSE}

library(texreg)

#OLS for number of calories on average

ols_model <- lm(CalorieTotal ~ Groups, data = df)
predicted_valuesOLS <- predict(ols_model,df)
df$predicted_ols <- predicted_valuesOLS
ggplot(df, aes(x=Groups, y=predicted_ols, color=Groups)) +
  geom_boxplot() +
  labs(title="Average number of calories by Treatment, OLS Model 0", x="Treatment", y="Av. number of calories")

ols_model10 <- lm(CalorieTotal ~ Groups*dprime1, data = df)
summary(ols_model10)

ols_model11 <- lm(CalorieTotal ~ Groups*dprime2, data = df)
summary(ols_model11)

ols_model12 <- lm(CalorieTotal ~ Groups*dprime3, data = df)
summary(ols_model12)

# Generate a table comparing the models  
screenreg(list(ols_model, ols_model10, ols_model11, ols_model12))  


Absent <- 400.098
Detailed <- 400.098 - 3.358
Coarse <- 400.098 - 5.577

Absent_Coarse <- ((Absent-Coarse)/Coarse)*100
Absent_Detailed <- ((Absent-Detailed)/Detailed)*100


library(effects)

# Plot the interaction effect:
plot(allEffects(ols_model10))
plot(allEffects(ols_model11))
plot(allEffects(ols_model12))


```

## Merging choice data sets by treatment groups

Same specification than before.

```{r logit, echo=FALSE}

library(tidyr)
library(dplyr)
library(readxl)

#selecting columns Coarse


dflogitnolabels <-  df %>%
  select(
    `Response ID` = `Response ID`,
    35:50,  # Choice task columns
    103:110, #calorie preferences
    126, 131, 136, 141, # additional shopping behavior children at home
    146, 195, 193, 194, 196, 125, # Additional demographic sex, age range, ethnicity, education level
    186, # choice task response time
    212, 221, 230, # working memory
    223, #new dprime3_20hits
    226, # new dprime3_10hits
    Groups
  )

#transpose data

dflogitlong_data <- dflogitnolabels %>%
  pivot_longer(
    cols = 2:17,
    names_to = "Choice",
    values_to = "CerealSelected"
    )


dflogitlong_data <- subset(dflogitlong_data, Groups == "Absent")

#selecting columns Coarse


dflogitcoarse  <-  df %>%
  select(
    `Response ID` = `Response ID`,
    53:68,  # Choice task columns
    103:110, #calorie preferences
    126, 131, 136, 141, # additional shopping behavior children at home
    146, 195, 193, 194, 196, 125, # Additional demographic sex, age range, ethnicity, education level
    186, # choice task response time
    212, 221, 230, # working memory
    223, #new dprime3_20hits
    226, # new dprime3_10hits
    Groups
  )

#transpose data

dflogitlong_data2 <- dflogitcoarse %>%
  pivot_longer(
    cols = 2:17,
    names_to = "Choice",
    values_to = "CerealSelected"
    )

# Sort by ID to make it easier to read
dflogitlong_data2 <- dflogitlong_data2 %>%
  arrange(`Response ID`)

dflogitlong_data2 <- subset(dflogitlong_data2, Groups == "Coarse")

#selecting columns Detailed

dflogitdetailed  <-  df %>%
  select(
    `Response ID` = `Response ID`,
    72:87,  # Choice task columns
    103:110, #calorie preferences
    126, 131, 136, 141, # additional shopping behavior children at home
    146, 195, 193, 194, 196, 125, # Additional demographic sex, age range, ethnicity, education level
    186, # choice task response time
    212, 221, 230, # working memory
    223, #new dprime3_20hits
    226, # new dprime3_10hits
    Groups
  )

#transpose data

dflogitlong_data3 <- dflogitdetailed %>%
  pivot_longer(
    cols = 2:17,
    names_to = "Choice",
    values_to = "CerealSelected"
    )

# Sort by ID to make it easier to read
dflogitlong_data3 <- dflogitlong_data3 %>%
  arrange(`Response ID`)

dflogitlong_data3 <- subset(dflogitlong_data3, Groups == "Detailed")

#Merge datasets

#using merge

merged_df <- rbind(dflogitlong_data, dflogitlong_data2, dflogitlong_data3)

#calculating n

sum(!is.na(merged_df$dprime1))
sum(!is.na(merged_df$dprime2))
sum(!is.na(merged_df$dprime3))
sum(!is.na(merged_df$dprime3_20hits))
sum(!is.na(merged_df$dprime3_10hits))


```

## Multilevel log-binomial regression Lmer - ATE, number of calories 


```{r multical, echo=FALSE}
library(texreg)
library(Matrix)
library(lme4)


# First, let's verify the variable is numeric and see its distribution
merged_df$CerealSelected <- as.numeric(merged_df$CerealSelected)

continuous <- lmer(CerealSelected ~ Groups + (1 | `Response ID`), 
                        data = merged_df)
# Fit the linear mixed model
continuous_model1 <- lmer(CerealSelected ~ Groups*dprime1 + (1 | `Response ID`), 
                        data = merged_df)
continuous_model2 <- lmer(CerealSelected ~ Groups*dprime2 + (1 | `Response ID`), 
                        data = merged_df)
continuous_model3 <- lmer(CerealSelected ~ Groups*dprime3 + (1 | `Response ID`), 
                        data = merged_df)
screenreg(list(continuous, continuous_model1, continuous_model2, continuous_model3))



```

## Multilevel log-binomial regression Lmer - ATE, number of calories + Prefences + Trails (for publication)

We checked multicolianearity, low colineariy without taking into account the interactions terms. But geeting fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
I did not include preference for cereal 5, and the error dissapeared

How to plot interactions: https://cran.r-project.org/web/packages/interactions/vignettes/interactions.html

subset_20hits <- df[df$hit2 >= 20, ] # Create a subset of participants who got at least 20 hits in 2-back
sum(!is.na(subset_20hits$hit3))



```{r multical1, echo=FALSE}

# Load required libraries
library(effects)
library(lattice)
library(gridExtra)
library(lme4)
library(texreg)

#library(ggpubr)
#ggarrange(weeds.bar.species, weeds.bar.soil, ncol = 2, nrow = 1)

# Fit the linear mixed model

colnames(merged_df)[c(2, 3, 4, 5, 6, 7, 8, 9)] <- c("r1", "r2", "r3", "r4","r5","r6","r7", "r8")

merged_df$Trials <- rep(1:16, length.out = nrow(merged_df))

c1 <- lmer(as.numeric(CerealSelected) ~ Groups + (1 | `Response ID`), data = merged_df, na.action = na.exclude)
c2 <- lmer(as.numeric(CerealSelected) ~ Groups + Trials + (1 | `Response ID`), data = merged_df, na.action = na.exclude)
c3 <- lmer(as.numeric(CerealSelected) ~ Groups +  Trials + r1 + r2 + r3 + r4+ r6+ r7+ r8 + (1 | `Response ID`), data = merged_df, na.action = na.exclude)
c4 <- lmer(as.numeric(CerealSelected)~ Groups*dprime1  + Trials + r1 + r2 + r3 + r4+ r6+ r7+ r8 + (1 | `Response ID`), data = merged_df, na.action = na.exclude)
c5 <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + Trials + r1 + r2 + r3 + r4+ r6+ r7+ r8 +  (1 | `Response ID`), data = merged_df, na.action = na.exclude)
c6 <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3  + Trials + r1 + r2 + r3 + r4+ r6+ r7+ r8 +  (1 | `Response ID`), data = merged_df, na.action = na.exclude)

screenreg(list(c1,c2,c3,c4,c5,c6))

library(performance)  
  # Check collinearity for the mixed-effects model directly  
print(check_collinearity(c2)) #nocollineary, this is not the problem

library(performance)  
  # Check collinearity for the mixed-effects model directly  
print(check_collinearity(c3)) #nocollineary, this is not the problem

library(performance)  
  # Check collinearity for the mixed-effects model directly  
print(check_collinearity(c4)) #nocollineary, this is not the problem

library(performance)  
  # Check collinearity for the mixed-effects model directly  
print(check_collinearity(c5)) #nocollineary, this is not the problem

library(performance)  
  # Check collinearity for the mixed-effects model directly  
print(check_collinearity(c6)) #nocollineary, this is not the problem

#htmlreg(  
  #list(c1,c2,c3,c4,c5,c6),  
  #file = "Lmer_regression_results.html",  
  #single.row = TRUE,  
  #custom.model.names = c("Model 1", "Model 2", "Model 3", "Model 4",  
                         #"Model 5", "Model 6"))  

latex_output <- capture.output(  
    texreg(list(c1, c2, c3, c4, c5, c6),  
           caption = "Regression Results",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("Model 1", "Model 2", "Model 3",   
                                "Model 4", "Model 5", "Model 6"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output, collapse = "\n"))  


```

## Multilevel log-binomial regression Lmer - ATE, number of calories + Prefences + Trails PLOTS


```{r mutiplot, echo=FALSE}

merged_df$predicted4 <- predict(c4)


# Box plot of model-predicted values by Groups (grayscale)
multi1 <- ggplot(merged_df, aes(x = Groups, y = predicted4, fill = Groups)) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  scale_fill_grey(start = 0.7, end = 0.3) +
  coord_cartesian(ylim = c(0, 500)) +
  theme_minimal() +
  labs(title = "Distribution of Model-Predicted Cereal Selection by Groups",
       x = "",
       y = "Calorie counts") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1), legend.position = "none")

multi1

merged_df$predicted5 <- predict(c5)


# Box plot of model-predicted values by Groups (grayscale)
multi2 <- ggplot(merged_df, aes(x = Groups, y = predicted5, fill = Groups)) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  scale_fill_grey(start = 0.7, end = 0.3) +
  coord_cartesian(ylim = c(0, 500)) +
  theme_minimal() +
  labs(title = "Distribution of Model-Predicted Cereal Selection by Groups",
       x = "",
       y = "Calorie counts") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1), legend.position = "none")

multi2

merged_df$predicted6 <- predict(c6)


# Box plot of model-predicted values by Groups (grayscale)
multi3 <- ggplot(merged_df, aes(x = Groups, y = predicted6, fill = Groups)) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  scale_fill_grey(start = 0.7, end = 0.3) +
  coord_cartesian(ylim = c(0, 500)) +
  theme_minimal() +
  labs(title = "Distribution of Model-Predicted Cereal Selection by Groups",
       x = "",
       y = "Calorie counts") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1), legend.position = "none")

  multi3

combined_plot_calorie <- arrangeGrob(multi1, multi2, multi3, ncol = 3)

# Save the plot
ggsave("combined_plot_calorie.png", combined_plot0, width = 12, height = 4, dpi = 300)


# Summarize predicted values by group
library(dplyr)
pred_summary <- merged_df %>%
  group_by(Groups) %>%
  summarise(
    mean_pred = mean(predicted4, na.rm = TRUE),
    se_pred = sd(predicted4, na.rm = TRUE) / sqrt(n())
  )

cal1 <- ggplot(pred_summary, aes(x = Groups, y = mean_pred, fill = Groups)) +
  geom_bar(stat = "identity", color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean_pred - se_pred, ymax = mean_pred + se_pred), width = 0.2) +
  scale_fill_grey(start = 0.7, end = 0.3) +
  coord_cartesian(ylim = c(0, 500)) + 
  theme_minimal() +
  labs(title = "1-Back",
       x = "",
       y = "Calories") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1), 
        legend.position = "none")

# Summarize predicted values by group
library(dplyr)
pred_summary1 <- merged_df %>%
  group_by(Groups) %>%
  summarise(
    mean_pred = mean(predicted5, na.rm = TRUE),
    se_pred = sd(predicted5, na.rm = TRUE) / sqrt(n())
  )

cal2 <- ggplot(pred_summary1, aes(x = Groups, y = mean_pred, fill = Groups)) +
  geom_bar(stat = "identity", color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean_pred - se_pred, ymax = mean_pred + se_pred), width = 0.2) +
  scale_fill_grey(start = 0.7, end = 0.3) +
  coord_cartesian(ylim = c(0, 500)) + 
  theme_minimal() +
  labs(title = "2-Back",
       x = "",
       y = "Calories") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1), 
        legend.position = "none")

# Summarize predicted values by group
library(dplyr)
pred_summary2 <- merged_df %>%
  group_by(Groups) %>%
  summarise(
    mean_pred = mean(predicted6, na.rm = TRUE),
    se_pred = sd(predicted6, na.rm = TRUE) / sqrt(n())
  )

cal3 <- ggplot(pred_summary2, aes(x = Groups, y = mean_pred, fill = Groups)) +
  geom_bar(stat = "identity", color = "black", width = 0.6) +
  geom_errorbar(aes(ymin = mean_pred - se_pred, ymax = mean_pred + se_pred), width = 0.2) +
  scale_fill_grey(start = 0.7, end = 0.3) +
  coord_cartesian(ylim = c(0, 500)) + 
  theme_minimal() +
  labs(title = "3-Back",
       x = "",
       y = "Calories") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1), 
        legend.position = "none")

combined_plot_caloriev2 <- arrangeGrob(cal1, cal2, cal3, ncol = 3)

# Save the plot
ggsave("combined_plot_caloriev2.png", combined_plot0, width = 12, height = 4, dpi = 300)




```

## Multilevel log-binomial regression Lmer - ATE, number of calories + Prefences ranking + Trails 

nothing is significant

```{r ranking, echo=FALSE}

# Create the ranking variable  
merged_df$RankingOfSelectedCereal <- NA  
  
# Define the vector of cereal calorie values that correspond to the healthiness columns  
cereals <- c(360, 374, 392, 398, 423, 431, 453, 470)  
  
# Loop over each row to assign the ranking for the selected cereal  
for(i in 1:nrow(merged_df)) {  
  selected_cereal <- merged_df$CerealSelected[i]  
    
  # If none option is selected, assign 0 preference  
  if(selected_cereal == "none" || is.na(selected_cereal)) {  
    merged_df$RankingOfSelectedCereal[i] <- 0  
  } else {  
    # Convert to numeric for matching with cereals vector  
    selected_cereal <- as.numeric(selected_cereal)  
    index <- match(selected_cereal, cereals)  
    if(!is.na(index)) {  
      ranking_col <- paste0("Cereal healthiness", index)  
      merged_df$RankingOfSelectedCereal[i] <- merged_df[[ranking_col]][i]  
    }  
  }  
}   

# Updated model using the ranking of the selected cereal  
c7 <- lmer(as.numeric(CerealSelected) ~   
                   Groups * dprime1 +   
                   RankingOfSelectedCereal +  # This is now meaningful for each choice  
                   Trials +   
                   (1 | `Response ID`),   
                   data = merged_df)  

# Updated model using the ranking of the selected cereal  
c8 <- lmer(as.numeric(CerealSelected) ~   
                   Groups * dprime2 +   
                   RankingOfSelectedCereal +  # This is now meaningful for each choice  
                   Trials +   
                   (1 | `Response ID`),   
                   data = merged_df)   
  
# Updated model using the ranking of the selected cereal  
c9 <- lmer(as.numeric(CerealSelected) ~   
                   Groups * dprime3 +    
                   RankingOfSelectedCereal +  # This is now meaningful for each choice  
                   Trials +   
                   (1 | `Response ID`),   
                   data = merged_df)    

screenreg(list(c7, c8, c9))


```




## Multilevel log-binomial regression Lmer - ATE, number of calories + covariates PLOTS

How to plot interactions: https://cran.r-project.org/web/packages/interactions/vignettes/interactions.html

subset_20hits <- df[df$hit2 >= 20, ] # Create a subset of participants who got at least 20 hits in 2-back
sum(!is.na(subset_20hits$hit3))


```{r plots2, echo=FALSE}

library(effects)
library(gridExtra)
library(grid)
library(ggplot2)

group_colors <- c("Absent" = "black", "Coarse" = "blue", "Detailed" = "red")

merged_df$pred_c4 <- predict(c4, re.form = NA)

e1 <- ggplot(merged_df, aes(x = Groups, y = pred_c4, fill = Groups)) +
  geom_boxplot(alpha = 0.6) +
  labs(title = "1-back n = 498",
       x = "",
       y = "Calorie counts") +
  scale_y_continuous(limits = c(200, 450)) +
  scale_x_discrete(labels = c("Absent", "Coarse", "Detailed")) +
  scale_fill_manual(values = group_colors) +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5))
  
merged_df$pred_c5 <- predict(c5, re.form = NA)

e2 <- ggplot(merged_df, aes(x = Groups, y = pred_c5, fill = Groups)) +
  geom_boxplot(alpha = 0.6) +
  labs(title = "2-back n = 464",
       x = "",
       y = "Calorie counts") +
  scale_y_continuous(limits = c(200, 450)) +
  scale_x_discrete(labels = c("Absent", "Coarse", "Detailed")) +
  scale_fill_manual(values = group_colors) +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5))
  

merged_df$pred_c6 <- predict(c6, re.form = NA)

e3 <- ggplot(merged_df, aes(x = Groups, y = pred_c6, fill = Groups)) +
  geom_boxplot(alpha = 0.6) +
  labs(title = "3-back n = 452",
       x = "",
       y = "Calorie counts") +
  scale_y_continuous(limits = c(200, 450)) +
  scale_x_discrete(labels = c("", "", "")) +
  scale_fill_manual(values = group_colors) +
  theme_minimal() +
 theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black"))

  
e1
e2
e3

combined_plot0 <- arrangeGrob(e1, e2, e3, ncol = 3)

# Save the plot
ggsave("combined_model.png", combined_plot0, width = 12, height = 4, dpi = 300)

print("Combined plot has been saved as combined_model.png")

#Plots

plot(effect("Groups*dprime1", c4), multiline = TRUE)
plot(effect("Groups*dprime2", c5), multiline = TRUE)
plot(effect("Groups*dprime3", c6), multiline = TRUE)


# Plot 1
p1 <- plot(effect("Groups*dprime1", c4), 
     main = "",
     xlab = "1-back",
     ylab = "Calorie counts",
     lines = list(multiline = TRUE, col = c("black", "blue", "red")),
     ci.style = "bands",
     rug = FALSE,
     grid = FALSE, 
     xlim = c(2, -15),
     ylim = c(200, 450))

p1

# Plot 2
p2 <- plot(effect("Groups*dprime2", c5), 
     main = "",
     xlab = "2-back",
     ylab = "Calorie counts",
     lines = list(multiline = TRUE, col = c("black", "blue", "red")),
     ci.style = "bands",
     rug = FALSE,
     grid = FALSE, 
     xlim = c(2, -15),
     ylim = c(200, 450))

p2

# Plot 3
p3 <- plot(effect("Groups*dprime3", c6), 
     main = "",
     xlab = "3-back",
     ylab = "Calorie counts",
     lines = list(multiline = TRUE, col = c("black", "blue", "red")),
     ci.style = "bands",
     rug = FALSE,
     grid = FALSE, 
     xlim = c(2, -15),
     ylim = c(200, 450))

p3

# Add a shared legend at the bottom
grid.text("Groups: Black = Label Absent, Blue = Coarse Label, Red = Detailed Label", 
          x = 0.5, y = 0.02, 
          just = "center",
          gp = gpar(fontsize = 10))

combined_plot <- arrangeGrob(p1, p2, p3, ncol = 3)

# Save the plot
ggsave("combined_nback_effects.png", combined_plot, width = 12, height = 4, dpi = 300)

print("Combined plot has been saved as combined_nback_effects.png")

```

## Multilevel log-binomial regression Lmer - Sensitivity analysis


```{r sensi, echo=FALSE}

 # Add Product 4 preference as a fixed effect  

 c5_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime1 + `Cereal healthiness4` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

   
 # With interaction to see if label effects differ by Product 4 preference  
 c6_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime1 + Groups*`Cereal healthiness4` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

 c7_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + `Cereal healthiness4` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

   
 # With interaction to see if label effects differ by Product 4 preference  
 c8_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + Groups*`Cereal healthiness4` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

 c9_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3 + `Cereal healthiness4` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

  # With interaction to see if label effects differ by Product 4 preference  
 c10_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3 + Groups*`Cereal healthiness4` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

   
 stargazer(c5_se, c6_se, c7_se,c8_se,c9_se,c10_se, title="Multilevel log-binomial regression", type="text")


  # Add Product 4 preference as a fixed effect  

 c11_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime1 + `Cereal healthiness6` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

   
 # With interaction to see if label effects differ by Product 4 preference  
 c12_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime1 + Groups*`Cereal healthiness6` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

 c13_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + `Cereal healthiness6` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

   
 # With interaction to see if label effects differ by Product 4 preference  
 c14_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + Groups*`Cereal healthiness6` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

 c15_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3 + `Cereal healthiness6` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

  # With interaction to see if label effects differ by Product 4 preference  
 c16_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3 + Groups*`Cereal healthiness6` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

   
 stargazer(c11_se, c12_se, c13_se,c14_se,c15_se,c16_se, title="Multilevel log-binomial regression", type="text")


  # Add Product 8 preference as a fixed effect  

 c17_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime1 + `Cereal healthiness8` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

   
 # With interaction to see if label effects differ by Product 4 preference  
 c18_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime1 + Groups*`Cereal healthiness8` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

 c19_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + `Cereal healthiness8` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

   
 # With interaction to see if label effects differ by Product 4 preference  
 c20_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + Groups*`Cereal healthiness8` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

 c21_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3 + `Cereal healthiness8` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude)  

  # With interaction to see if label effects differ by Product 4 preference  
 c22_se <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3 + Groups*`Cereal healthiness8` +   
            (1 | `Response ID`), data = merged_df, na.action = na.exclude) 

   
 stargazer(c17_se, c18_se, c19_se,c20_se,c21_se,c22_se, title="Multilevel log-binomial regression", type="text")

 
 
```


## Multilevel log-binomial regression Lmer - ATE, number of calories + covariates + reanalizing 3-back test 20 hits


```{r multical1, echo=FALSE}

# Load required libraries
library(effects)
library(lattice)
library(gridExtra)

#library(ggpubr)
#ggarrange(weeds.bar.species, weeds.bar.soil, ncol = 2, nrow = 1)


# Fit the linear mixed model

c44 <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3_20hits + Loseweight + Children + Responsable + (1 | `Response ID`), data = merged_df, na.action = na.exclude)
c55 <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3_10hits + Loseweight + Children + Responsable + (1 | `Response ID`), data = merged_df, na.action = na.exclude)
stargazer(c1,c2,c3, c4,c44,c55, title="Multilevel log-binomial regression", type="text")


```
 
## OLS - ATE, response time + with and without covariates

Same specification than before.

```{r multitime, echo=FALSE}

# First, let's verify the variable is numeric and see its distribution
df$`Duration Test (Min)` <- as.numeric(as.character(df$`Duration Test (Min)`))

time0 <- lm(`Duration Test (Min)` ~ Groups, data = df)


# Fit the linear mixed model
time1 <- lm(`Duration Test (Min)` ~ Groups*dprime1, data = df)
summary(time1)
time2 <- lm(`Duration Test (Min)` ~ Groups*dprime2, data = df)
summary(time2)
time3 <- lm(`Duration Test (Min)` ~ Groups*dprime3, data = df)
summary(time3)

screenreg(list(time1, time2, time3))

library(effects)

# Plot the interaction effect:
plot(allEffects(time1))
plot(allEffects(time2))
plot(allEffects(time3))

# Fit the linear mixed model + covariates

time0a <- lm(`Duration Test (Min)` ~ Groups*dprime1  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8`, data = df)
time1b <- lm(`Duration Test (Min)`~ Groups*dprime2  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8`, data = df)
time1c <- lm(`Duration Test (Min)`~ Groups*dprime3  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8`, data = df)

screenreg(list(time0, time0a, time1b, time1b, time1c))


```

## OLS - ATE, Log response time + covariates


```{r multitime2, echo=FALSE}


df$logtime <- log(df$`Duration Test (Min)`)

time00 <- lm(logtime ~ Groups, data = df)
time1aa <- lm(logtime~ Groups*dprime1  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8`, data = df)
time2bb <- lm(logtime ~ Groups*dprime2  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8`, data = df)
time3cc <- lm(logtime ~ Groups*dprime3  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8`, data = df)

screenreg(list(time00, time1aa, time2bb, time3cc))

latex_output_time <- capture.output(  
    texreg(list(time00, time1aa, time2bb, time3cc),  
           caption = "OLS Regression Results",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("Model 1", "Model 2", "Model 3", "Model 4"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output_time, collapse = "\n"))  

mean(df$`Cereal healthiness1`)
mean(df$`Cereal healthiness2`)
mean(df$`Cereal healthiness3`)
mean(df$`Cereal healthiness4`)
mean(df$`Cereal healthiness5`)
mean(df$`Cereal healthiness6`)
mean(df$`Cereal healthiness7`)
mean(df$`Cereal healthiness8`)



```



## Check variation in the outcome across groups to fit Glmer/Lmer

The Chi-squared test result you got (X-squared = 5.2995, df = 2, p-value = 0.07067) tells us about the relationship between the treatment groups and cereal selection. Let's break this down:

**What the test measures:**
- Tests whether there's a significant association between group membership (absent/coarse/detailed) and cereal selection (360-calorie selected or not)
- Null hypothesis (H0): No association between groups and selection
- Alternative hypothesis (Ha): There is an association

**Your results:**
- X-squared = 5.2995: The test statistic
- df = 2: Degrees of freedom (for 3 groups: (3-1) × (2-1) = 2)
- p-value = 0.07067: The probability value

**Interpretation:**
- Since p-value (0.07067) > 0.05 (conventional significance level), we fail to reject the null hypothesis
- However, p < 0.10 suggests a marginal or trending effect
- This means there's some evidence of differences between groups, but it's not strong enough to meet the conventional 0.05 threshold

**What this means for your study:**
1. There's some variation across groups (as evidenced by the trending p-value)
2. The differences between groups are subtle rather than dramatic
3. This supports using a more sophisticated analysis (like your GLMER) which can:
   - Account for individual differences
   - Include additional predictors
   - Model interactions
   - Handle repeated measures

```{r variation, echo=FALSE}


# 1. Create a contingency table of Groups by cereal360_selected  
print("Contingency table of cereal selection by group:")  
group_outcome_table <- table(merged_df_clean$Groups, merged_df_clean$cereal360_selected)  
print(group_outcome_table)  
  
# 2. Calculate proportions within each group  
print("\nProportions within each group:")  
prop_table <- prop.table(group_outcome_table, margin = 1) * 100  # margin=1 for row percentages  
print(prop_table)  
  
# 3. Chi-square test for independence  
print("\nChi-square test of independence:")  
chisq_test <- chisq.test(group_outcome_table)  
print(chisq_test)  
  
# 4. Visual check with a bar plot  
library(ggplot2)  
ggplot(merged_df_clean, aes(x = Groups, fill = factor(cereal360_selected))) +  
  geom_bar(position = "fill") +  
  labs(y = "Proportion",   
       title = "Proportion of Cereal Selection by Group",  
       fill = "360-calorie Selected") +  
  theme_minimal()  

```


## Generalized logit mixed-effects or Multilevel Glmer - ATE, probability of selecting a product + dprime3 + Trial specification

Redo table 6 by including a specification that takes into account only trials that include the cereal brand to be predicted. I splited the datasets to take into account the specific trails. Otherwise, the regression is based on a database with many zeros, which may affect the results. In addition, it takes into account only those number of observations for the cereal of interest, which reduces the number of observations by half. 

I have included preferences for each specific cereal as well.

Options 'Prefer  not to say' were recoded as missing values because the few observations of this variable makes the model to fail in convergence.

After taking all these details the model fit works better. Model 0 does not include preferences.

```{r multilogit4, echo=FALSE}


# Create a new column that cycles through 1 to 16 for each row
merged_df$Trials <- rep(1:16, length.out = nrow(merged_df))

 # Write the fixed dataframe to CSV  
#write.csv(merged_df, "merged_df.csv", row.names = FALSE) 

subset_df360 <- merged_df[merged_df$Trials %in% 9:16, ]
subset_df374 <- merged_df[merged_df$Trials %in% 1:8, ]
subset_df392 <- merged_df[merged_df$Trials %in% c(1,2,3,4,9,10,11,12), ]
subset_df398 <- merged_df[merged_df$Trials %in% c(5,6,7,8,13,14,15,16), ]
subset_df423 <- merged_df[merged_df$Trials %in% c(1,2,5,6,9,10,13,14), ]
subset_df431 <- merged_df[merged_df$Trials %in% c(1,3,5,7,9,11,13,15), ]
subset_df453 <- merged_df[merged_df$Trials %in% c(3,4,7,8,11,12,15,16), ]
subset_df470 <- merged_df[merged_df$Trials %in% c(2,4,6,8,10,12,14,16), ]

control = glmerControl(optimizer = "Nelder_Mead",   
                       optCtrl = list(maxfun = 100000),  
                       tolPwrss = 1e-4,  # Default is usually 1e-7  
                       check.conv.grad = .makeCC("warning", tol = 0.05, relTol = NULL))  # Increase tolerance to 0.05  

t1 <- glmer(CerealSelected == 0 ~ Groups * dprime3 + (1 | `Response ID`),
                family = binomial("logit"), 
                data = merged_df)

t2 <- glmer(CerealSelected == 360 ~ Groups * dprime3 + `Cereal healthiness1` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df360)
summary(t2)

t3 <- glmer(CerealSelected == 374 ~ Groups * dprime3 + `Cereal healthiness2` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df374)

t4 <- glmer(CerealSelected == 392 ~ Groups * dprime3 +  `Cereal healthiness3` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df392)

t5 <- glmer(CerealSelected == 398 ~ Groups * dprime3  + `Cereal healthiness4` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df398)

t6 <- glmer(CerealSelected == 423 ~ Groups * dprime3  + `Cereal healthiness5` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df423)

t7 <- glmer(CerealSelected == 431 ~ Groups * dprime3 + `Cereal healthiness6` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df431)

t8 <- glmer(CerealSelected == 453 ~ Groups * dprime3 + `Cereal healthiness7` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df453)

t9 <- glmer(CerealSelected == 470 ~ Groups * dprime3  + `Cereal healthiness8` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df470)

screenreg(list(t1, t2, t3, t4, t5, t6, t7, t8, t9))



```


## Converge issue - different optimizer and increased iterations (bobyqa)

The previous model was based on a sub sample that included the trials of interest (For example, for Cereal A 360). But the sub sample means that the observations decreased by half. NOw, I fir a model considering the full sample. I identified the trials where the Cereal A 360 (the probability to be estimated) is included (9 to 16). This represents 3985 observations, and amog these observations, 1348 represent the selection of Cereal A, 34%. This model explains the probability of selecting cereal A across all trials where the model controls for the present of Cereal A.

I have got problem with converge, I have rescale dprime3, but I am getting this issue. I have checked collinearity among predictor without interaction term, no collinearity. Rescale the dprime 3 did not work, and I dont want to do it because it z values, I am mot confident to rescale, but I have scale healthiness. Finally, the model fits well when I have included different optimizer and increased iterations (bobyqa). 



```{r converge, echo=FALSE}

merged_df <- merged_df %>%  
  mutate(  
    # Set indicator for trials 9-16 using existing Trials column  
    cereal360_available = ifelse(Trials >= 9 & Trials <= 16, 1, 0),  
    # Binary outcome for 360-calorie cereal selection  
    cereal360_selected = ifelse(CerealSelected == 360, 1, 0)  
  )  

table(merged_df$Trials, merged_df$CerealSelected)
table(merged_df$Trials, merged_df$cereal360_available)
table(merged_df$Trials, merged_df$cereal360_selected)

converge <- glmer(cereal360_selected ~ Groups + `Cereal healthiness1` + cereal360_available +  (1 | `Response ID`),
                family = binomial("logit"), 
                data = merged_df_clean)
summary(converge)


library(performance)  
  # Check collinearity for the mixed-effects model directly  
print(check_collinearity(t22)) #nocollineary, this is not the problem

#Not including missing values and scale healthiness preferences
print(sum(is.na(merged_df$dprime3))) 

merged_df_clean <- merged_df %>%  
  filter(!is.na(dprime3)) %>%  
  mutate(  
    healthiness_scaled = scale(`Cereal healthiness1`)  
  ) 

converge1 <- glmer(cereal360_selected ~ Groups*dprime3 + healthiness_scaled + cereal360_available +  (1 | `Response ID`),
                family = binomial("logit"), 
                data = merged_df_clean)
summary(converge1) # I am still getting problems with converge

#Not including missing values, scale healthiness, change optimazer and more iterations according to Julius

converge2 <- glmer(cereal360_selected ~ Groups*dprime3 + healthiness_scaled + cereal360_available +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df_clean)
summary(converge2) # FINALLY WORKS


converge3 <- glmer(cereal360_selected ~ Groups*dprime3 + healthiness_scaled + cereal360_available +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "Nelder_Mead",  
                                        optCtrl = list(maxfun = 50000)), 
                data = merged_df_clean)
summary(converge3) 

# Run a simple logistic regression model without random effects  
simple_model <- glm(cereal360_selected ~ Groups*dprime3 + healthiness_scaled + cereal360_available,  
                    family = binomial("logit"),  
                    data = merged_df_clean)  
summary(simple_model) 

# Run a simple logistic regression model without random effects  
simple_model2 <- glm(cereal360_selected ~ Groups*dprime3 + healthiness_scaled + Trials,  
                    family = binomial("logit"),  
                    data = merged_df_clean)  
summary(simple_model2) 

converge4 <- glmer(cereal360_selected ~ Groups*dprime3 + healthiness_scaled + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "Nelder_Mead",  
                                        optCtrl = list(maxfun = 50000)), 
                data = merged_df_clean)
summary(converge4) 

converge5 <- glmer(cereal360_selected ~ Groups*dprime3 + healthiness_scaled + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df_clean)
summary(converge5) 

t2v2 <- glmer(CerealSelected == 360 ~ Groups * dprime3 + `Cereal healthiness1` + (1 | `Response ID`),
                family = binomial("logit"), 
                data = subset_df360)

screenreg(list(converge, converge1, converge2, converge3, simple_model, simple_model2, converge4, converge5, t2))


htmlreg(  
  list(converge, converge1, converge2, converge3, simple_model, simple_model2, converge4, converge5, t2),  
  file = "comparison_regression_results.html",  
  single.row = TRUE,  
  custom.model.names = c("C.Ava-No d'", "C.Ava", "bobyqa", "Nelder_Mead",  
                         "C.Ava Logit", "Trials Logit", "Trials Nelder_Mead", "bobyqa_Mead","Subsample")  
)  
  
# Confirmation message  
print("Comparison regressions table to regression_results.html")  


```

## Generalized logit mixed-effects or Multilevel Glmer - ATE, probability of selecting a product + dprime3 + Cereal available as an indicator + bobyqa

I have tried bobyqa as optimazer, it did not work, same problems with convergence.

The previous model was based on a sub sample that included the trials of interest (For example, for Cereal A 360). But the sub sample means that the observations decreased by half. NOw, I fir a model considering the full sample. I identified the trials where the Cereal A 360 (the probability to be estimated) is included (9 to 16). This represents 3985 observations, and amog these observations, 1348 represent the selection of Cereal A, 34%. This model explains the probability of selecting cereal A across all trials where the model controls for the present of Cereal A.

I have got problem with converge, I have rescale dprime3, but I am getting this issue. I have checked collinearity among predictor without interaction term, no collinearity. Rescale the dprime 3 did not work, and I dont want to do it because it z values, I am mot confident to rescale, but I have scale healthiness. Finally, the model fits well when I have included different optimizer and increased iterations (bobyqa). 


```{r multilogit5, echo=FALSE}


t11 <- glmer(CerealSelected == 0 ~ Groups * dprime3 + healthiness_scaled +  (1 | `Response ID`),
                family = binomial("logit"), 
                data = merged_df_clean)


merged_df_clean <- merged_df %>%  
  # Create binary indicators  
  mutate(  
    cereal392_available = ifelse(c(1,2,3,4,9,10,11,12), 1, 0),  
    cereal392_selected = ifelse(CerealSelected == 392, 1, 0)  
  ) %>%  
  # Remove NA values from dprime3  
  filter(!is.na(dprime3)) %>%  
  # Scale continuous variables  
  mutate(  
    dprime3_scaled = scale(dprime3),  
    healthiness_scaled1 = scale(`Cereal healthiness1`)  
  )  
  
# 2. Fit the model with correct control parameters  
t392 <- glmer(cereal374_selected ~ Groups * dprime3_scaled +   
             healthiness_scaled3 + cereal374_available +   
             (1 | `Response ID`),  
           family = binomial("logit"),  
           control = glmerControl(optimizer = "bobyqa",  
                                optCtrl = list(maxfun = 200000),  
                                check.conv.grad = .makeCC("warning", tol = 0.005)),  
           data = merged_df_clean)  
  
# 3. Check the summary  
print(summary(t392)) 


```
## Generalized logit mixed-effects or Multilevel Glmer - ATE, probability of selecting a product + dprime3 + Trial as an indicator for cereal availability + bobyqa

For g0, i did not include preference for cereal 5, for converge issues, but i included all the preferences then. I tested the model with and without the preferences and the coefficient were almost the same, SE stable

```{r back3, echo=FALSE}

library(dplyr)

merged_df <- merged_df %>%  
  mutate(cereal0_selected = ifelse(CerealSelected == 0, 1, 0)) 

g0 <- glmer(cereal0_selected ~ Groups*dprime3 + `Cereal healthiness1`+ `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7` + `Cereal healthiness8`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

merged_df <- merged_df %>%  
  mutate(cereal360_selected = ifelse(CerealSelected == 360, 1, 0)) 

g360 <- glmer(cereal360_selected ~ Groups*dprime3 + `Cereal healthiness1` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

merged_df <- merged_df %>%  
  mutate(cereal374_selected = ifelse(CerealSelected == 374, 1, 0)) 

g374 <- glmer(cereal374_selected ~ Groups*dprime3 + `Cereal healthiness2`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


merged_df <- merged_df %>%  
  mutate(cereal392_selected = ifelse(CerealSelected == 392, 1, 0))  

g392 <- glmer(cereal392_selected ~ Groups*dprime3 + `Cereal healthiness3`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


merged_df <- merged_df %>%   
  mutate(cereal398_selected = ifelse(CerealSelected == 398, 1, 0))  

g398 <- glmer(cereal398_selected ~ Groups*dprime3 + `Cereal healthiness4` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

merged_df <- merged_df %>%  
  mutate(cereal423_selected = ifelse(CerealSelected == 423, 1, 0))  

g423 <- glmer(cereal423_selected ~ Groups*dprime3 + `Cereal healthiness5` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

merged_df <- merged_df %>%   
  mutate(cereal431_selected = ifelse(CerealSelected == 431, 1, 0))  

g431 <- glmer(cereal431_selected ~ Groups*dprime3 + `Cereal healthiness6` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

merged_df <- merged_df %>%  
  mutate(cereal453_selected = ifelse(CerealSelected == 453, 1, 0))  

g453 <- glmer(cereal453_selected ~ Groups*dprime3 + `Cereal healthiness7` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

merged_df <- merged_df %>%  
  mutate(cereal470_selected = ifelse(CerealSelected == 470, 1, 0))  

g470 <- glmer(cereal470_selected ~ Groups*dprime3 + `Cereal healthiness8` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

table(merged_df_clean$CerealSelected, merged_df_clean$Groups)

screenreg(list(g0, g360, g374, g392, g398, g423, g431, g453, g470))

#htmlreg(  
 # list(g360, g374, g392, g398, g423, g431, g453, g470),  
  #file = "regression_results.html",  
  #single.row = TRUE,  
  #custom.model.names = c("Model 1", "Model 2", "Model 3", "Model 4",  
                         #"Model 5", "Model 6", "Model 7", "Model 8")  
#)  
  
# Confirmation message  
#print("Exported regression table to regression_results.html")  

latex_output <- capture.output(  
    texreg(list(g0, g360, g374, g392, g398, g423, g431, g453, g470),  
           caption = "Glmer Regression Results",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("0", "360", "374", "392",   
                                "398", "423", "431", "453", "470"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output, collapse = "\n"))  



```

## Generalized logit mixed-effects or Multilevel Glmer - ATE, probability of selecting a product + dprime2 and dprime1 + Trial as an indicator for cereal availability + bobyqa (for publication)


```{r back2, echo=FALSE}

g0b <- glmer(cereal0_selected ~ Groups*dprime2 + `Cereal healthiness1`+ `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7` + `Cereal healthiness8`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g360b <- glmer(cereal360_selected ~ Groups*dprime2 + `Cereal healthiness1` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g374b <- glmer(cereal374_selected ~ Groups*dprime2 + `Cereal healthiness2`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g392b <- glmer(cereal392_selected ~ Groups*dprime2 + `Cereal healthiness3`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g398b <- glmer(cereal398_selected ~ Groups*dprime2 + `Cereal healthiness4` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g423b <- glmer(cereal423_selected ~ Groups*dprime2 + `Cereal healthiness5` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g431b <- glmer(cereal431_selected ~ Groups*dprime2 + `Cereal healthiness6` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g453b <- glmer(cereal453_selected ~ Groups*dprime2 + `Cereal healthiness7` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g470b <- glmer(cereal470_selected ~ Groups*dprime2 + `Cereal healthiness8` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

screenreg(list(g0b, g360b, g374b, g392b, g398b, g423b, g431b, g453b, g470b))


latex_output3 <- capture.output(  
    texreg(list(g0b, g360b, g374b, g392b, g398b, g423b, g431b, g453b, g470b),  
           caption = "Glmer Regression Results 2-back",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("0", "360", "374", "392",   
                                "398", "423", "431", "453", "470"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output3, collapse = "\n"))  

g0c <- glmer(cereal0_selected ~ Groups*dprime1 + `Cereal healthiness1`+ `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7` + `Cereal healthiness8` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g360c <- glmer(cereal360_selected ~ Groups*dprime1 + `Cereal healthiness1` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g374c <- glmer(cereal374_selected ~ Groups*dprime1 + `Cereal healthiness2`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g392c <- glmer(cereal392_selected ~ Groups*dprime1 + `Cereal healthiness3`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g398c <- glmer(cereal398_selected ~ Groups*dprime1 + `Cereal healthiness4` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g4231 <- glmer(cereal423_selected ~ Groups*dprime1 + `Cereal healthiness5` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g431c <- glmer(cereal431_selected ~ Groups*dprime1 + `Cereal healthiness6` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g453c <- glmer(cereal453_selected ~ Groups*dprime1 + `Cereal healthiness7` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g470c <- glmer(cereal470_selected ~ Groups*dprime1 + `Cereal healthiness8` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

screenreg(list(g0c, g360c, g374c, g392c, g398c, g4231, g431c, g453c, g470c))

table(merged_df$CerealSelected, merged_df$Groups)

latex_output4 <- capture.output(  
    texreg(list(g0c, g360c, g374c, g392c, g398c, g4231, g431c, g453c, g470c),  
           caption = "Glmer Regression Results n-back1",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("0", "360", "374", "392",   
                                "398", "423", "431", "453", "470"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output4, collapse = "\n"))  

```

## Generalized logit mixed-effects or Multilevel Glmer - ATE, probability of selecting a product + no nback + Trial as an indicator for cereal availability + bobyqa (For publication)

```{r noback, echo=FALSE}

library(texreg)

g0d <- glmer(cereal0_selected ~ Groups + `Cereal healthiness1`+ `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7` + `Cereal healthiness8` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g360d <- glmer(cereal360_selected ~ Groups + `Cereal healthiness1` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g374d <- glmer(cereal374_selected ~ Groups + `Cereal healthiness2`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g392d <- glmer(cereal392_selected ~ Groups + `Cereal healthiness3`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g398d <- glmer(cereal398_selected ~ Groups + `Cereal healthiness4` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g423d <- glmer(cereal423_selected ~ Groups + `Cereal healthiness5` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g431d <- glmer(cereal431_selected ~ Groups + `Cereal healthiness6` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g453d <- glmer(cereal453_selected ~ Groups + `Cereal healthiness7` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g470d <- glmer(cereal470_selected ~ Groups + `Cereal healthiness8` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

screenreg(list(g0d, g360d, g374d, g392d, g398d, g423d, g431d, g453d, g470d))

latex_output <- capture.output(  
    texreg(list(g0d, g360d, g374d, g392d, g398d, g423d, g431d, g453d, g470d),  
           caption = "Glmer Regression Results 2",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("0", "360", "374", "392",   
                                "398", "423", "431", "453", "470"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output, collapse = "\n"))  


```

## Generalized logit mixed-effects or Multilevel Glmer - ATE, probability of selecting a product + nback no preferences + Trial as an indicator for cereal availability + bobyqa

```{r nopref, echo=FALSE}

g0e <- glmer(cereal0_selected ~ Groups*dprime3 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g360e <- glmer(cereal360_selected ~ Groups*dprime3  + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g374e <- glmer(cereal374_selected ~ Groups*dprime3 +  Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g392e <- glmer(cereal392_selected ~ Groups*dprime3 +  Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g398e <- glmer(cereal398_selected ~ Groups*dprime3  + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g423e <- glmer(cereal423_selected ~ Groups*dprime3  + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g431e <- glmer(cereal431_selected ~ Groups*dprime3 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g453e <- glmer(cereal453_selected ~ Groups*dprime3 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g470e <- glmer(cereal470_selected ~ Groups*dprime3 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

screenreg(list(g0e, g360e, g374e, g392e, g398e, g423e, g431e, g453e, g470e))

latex_output5 <- capture.output(  
    texreg(list(g0e, g360e, g374e, g392e, g398e, g423e, g431e, g453e, g470e),  
           caption = "Glmer Regression Results 2",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("0", "360", "374", "392",   
                                "398", "423", "431", "453", "470"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output5, collapse = "\n")) 

g0f <- glmer(cereal0_selected ~ Groups*dprime2 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g360f <- glmer(cereal360_selected ~ Groups*dprime2  + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g374f <- glmer(cereal374_selected ~ Groups*dprime2 +  Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g392f <- glmer(cereal392_selected ~ Groups*dprime2 +  Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g398f <- glmer(cereal398_selected ~ Groups*dprime2  + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g423f <- glmer(cereal423_selected ~ Groups*dprime2  + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g431e <- glmer(cereal431_selected ~ Groups*dprime2 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)


g453f <- glmer(cereal453_selected ~ Groups*dprime2 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

g470f <- glmer(cereal470_selected ~ Groups*dprime2 + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = merged_df, 
                na.action = na.exclude)

screenreg(list(g0f, g360f, g374f, g392f, g398f, g423f, g431f, g453f, g470f))

latex_output6 <- capture.output(  
    texreg(list(g0f, g360f, g374f, g392f, g398f, g423f, g431f, g453f, g470f),  
           caption = "Glmer Regression Results 2",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("0", "360", "374", "392",   
                                "398", "423", "431", "453", "470"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output6, collapse = "\n"))


```

## Multilevel log-binomial regression Lmer  - ATE, Sensitivity analysis, propensity n-back reduction size

1. What is the Propensity to Progress? The “propensity of progressing to the next level” refers to the probability that a participant advances from, say, 1-back to 2-back, or from 2-back to 3-back, given their observed characteristics (e.g., demographics, baseline cognitive ability, group assignment, etc.). This is typically estimated using a logistic regression, where the outcome is whether the participant progressed (1) or not (0). IT DID NOT WORK, FEW MISSING DATA

2. Imputation. Multiple imputation (MI) is a valid and widely accepted methodology for handling missing data in randomized controlled trials (RCTs), including for journals like BMC Public Health. In fact, MI is often recommended by CONSORT guidelines and leading statistical authorities for RCTs, especially when missing data are not negligible and the missingness mechanism is plausibly Missing At Random (MAR). 

```{r sensi1, echo=FALSE}

##MATCHED SAMPLE

complete_cases <- merged_df[!is.na(merged_df$dprime1) & !is.na(merged_df$dprime2) & !is.na(merged_df$dprime3), ]

cc1 <- lmer(as.numeric(CerealSelected) ~ Groups + (1 | `Response ID`), data = complete_cases, na.action = na.exclude)
cc2 <- lmer(as.numeric(CerealSelected) ~ Groups + Trials + (1 | `Response ID`), data = complete_cases, na.action = na.exclude)
cc3 <- lmer(as.numeric(CerealSelected) ~ Groups + Trials + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8` + (1 | `Response ID`), data = complete_cases, na.action = na.exclude)
cc4 <- lmer(as.numeric(CerealSelected)~ Groups*dprime1  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8` + Trials + (1 | `Response ID`), data = complete_cases, na.action = na.exclude)
cc5 <- lmer(as.numeric(CerealSelected) ~ Groups*dprime2 + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+`Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8` + Trials + (1 | `Response ID`), data = complete_cases, na.action = na.exclude)
cc6 <- lmer(as.numeric(CerealSelected) ~ Groups*dprime3  + `Cereal healthiness1` + `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7`+ `Cereal healthiness8` + Trials + (1 | `Response ID`), data = complete_cases, na.action = na.exclude)

screenreg(list(cc1,cc2,cc3,cc4,cc5,cc6))

latex_output_sensi <- capture.output(  
    texreg(list(cc1,cc2,cc3,cc4,cc5,cc6),  
           caption = "Regression Results",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("Model 1", "Model 2", "Model 3",   
                                "Model 4", "Model 5", "Model 6"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_output_sensi, collapse = "\n"))  


##PROPENSITY

library(dplyr)

colnames(df)[c(9)] <- c("ID")
colnames(merged_df)[c(1)] <- c("ID")

# Calculate propensity scores at participant level first
df <- df %>%
  group_by(ID) %>%
  slice(1) %>%  # Take first observation per participant
  mutate(
    progressed_to_2back = as.integer(!is.na(dprime2)),
    progressed_to_3back = as.integer(!is.na(dprime3))
  ) %>%
  ungroup()

# Fit the models
model_2back <- glm(progressed_to_2back ~ Sex + Age2 + Ethnicity_reco + Level_Education2 + Groups + dprime1,
                   data = df, family = binomial)

model_3back <- glm(progressed_to_3back ~ Sex + Age2 + Ethnicity_reco + Level_Education2 + Groups + dprime2,
                   data = df, family = binomial)

screenreg(list(model_2back, model_3back))


```
## Generalized logit mixed-effects or Multilevel Glmer - ATE, probability of selecting a product + dprime2 + Trial as an indicator for cereal availability + bobyqa + sensitivity analysis


```{r sensi3, echo=FALSE}

library(dplyr)

complete_cases <- complete_cases %>%  
  mutate(cereal0_selected = ifelse(CerealSelected == 0, 1, 0)) 

gg0 <- glmer(cereal0_selected ~ Groups*dprime2 + `Cereal healthiness1`+ `Cereal healthiness2`+ `Cereal healthiness3`+ `Cereal healthiness4`+ `Cereal healthiness6`+ `Cereal healthiness7` + `Cereal healthiness8`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)

complete_cases <- complete_cases %>%  
  mutate(cereal360_selected = ifelse(CerealSelected == 360, 1, 0)) 

gg360 <- glmer(cereal360_selected ~ Groups*dprime2 + `Cereal healthiness1` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)

complete_cases <- complete_cases %>%  
  mutate(cereal374_selected = ifelse(CerealSelected == 374, 1, 0)) 

gg374 <- glmer(cereal374_selected ~ Groups*dprime2 + `Cereal healthiness2`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)


complete_cases <- complete_cases %>%  
  mutate(cereal392_selected = ifelse(CerealSelected == 392, 1, 0))  

gg392 <- glmer(cereal392_selected ~ Groups*dprime2 + `Cereal healthiness3`+ Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)


complete_cases <- complete_cases %>%   
  mutate(cereal398_selected = ifelse(CerealSelected == 398, 1, 0))  

gg398 <- glmer(cereal398_selected ~ Groups*dprime2 + `Cereal healthiness4` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)

complete_cases <- complete_cases %>%  
  mutate(cereal423_selected = ifelse(CerealSelected == 423, 1, 0))  

gg423 <- glmer(cereal423_selected ~ Groups*dprime2 + `Cereal healthiness5` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)

complete_cases <- complete_cases %>%   
  mutate(cereal431_selected = ifelse(CerealSelected == 431, 1, 0))  

gg431 <- glmer(cereal431_selected ~ Groups*dprime2 + `Cereal healthiness6` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)

complete_cases <- complete_cases %>%  
  mutate(cereal453_selected = ifelse(CerealSelected == 453, 1, 0))  

gg453 <- glmer(cereal453_selected ~ Groups*dprime2 + `Cereal healthiness7` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)

complete_cases <- complete_cases %>%  
  mutate(cereal470_selected = ifelse(CerealSelected == 470, 1, 0))  

gg470 <- glmer(cereal470_selected ~ Groups*dprime2 + `Cereal healthiness8` + Trials +  (1 | `Response ID`),
                family = binomial("logit"),
              control = glmerControl(optimizer = "bobyqa",  
                                     optCtrl = list(maxfun = 200000)),
                data = complete_cases, 
                na.action = na.exclude)

screenreg(list(gg0, gg360, gg374, gg392, gg398, gg423, gg431, gg453, gg470))

latex_outputsensi_2back <- capture.output(  
    texreg(list(gg0, gg360, gg374, gg392, gg398, gg423, gg431, gg453, gg470),  
           caption = "Glmer Regression Results",  
           label = "tab:regression",  
           booktabs = TRUE,  
           dcolumn = TRUE,  
           use.packages = TRUE,  
           float.pos = "h!",  
           stars = c(0.01, 0.05, 0.1),  # Customize significance stars  
           custom.model.names = c("0", "360", "374", "392",   
                                "398", "423", "431", "453", "470"),  
           digits = 2)  # Number of decimal places  
)  
  
# Print the LaTeX code  
cat(paste(latex_outputsensi_2back, collapse = "\n"))  


```



## statistics for publication

```{r stat1, echo=FALSE}

dprime3_stats <- aggregate(dprime3 ~ Groups, data = df, 
                         FUN = function(x) c(mean = mean(x, na.rm = TRUE), 
                                           sd = sd(x, na.rm = TRUE)))
print(dprime3_stats)

cross_tab4 <- table(df$`Are there children in your household?`, df$Groups)

# Add percentages to the table
cross_tab4_percent <- prop.table(cross_tab4, margin = 2) * 100
print(cross_tab4_percent)

cross_tab5 <- table(df$`Are you responsible for household purchases?`, df$Groups)
print(cross_tab5)

# Add percentages to the table
cross_tab5_percent <- prop.table(cross_tab5, margin = 2) * 100
print(cross_tab5_percent)

cross_tab6 <- table(df$FamiliarityBrands, df$Groups)
print(cross_tab6)

# Add percentages to the table
cross_tab6_percent <- prop.table(cross_tab6, margin = 2) * 100
print(cross_tab6_percent)

cross_tab7 <- table(df$`On a scale of 1 to 5, how would you rate the amount of information you had to choose cereals according to your nutritional preferences? Where 5 means information overload and 1 means insufficient information.`, df$Groups)
print(cross_tab7)

# Add percentages to the table
cross_tab7_percent <- prop.table(cross_tab7, margin = 2) * 100
print(cross_tab7_percent)

cross_tab8 <- table(df$`On a scale of 1 to 5, how much did you notice the labels on the cereal packages during the experiment? Where 5 means always and 1 means never....69`, df$Groups)
print(cross_tab8)

# Add percentages to the table
cross_tab8_percent <- prop.table(cross_tab8, margin = 2) * 100
print(cross_tab8_percent)

cross_tab9 <- table(df$`On a scale of 1 to 5, how much did you notice the labels on the cereal packages during the experiment? Where 5 means always and 1 means never....88`, df$Groups)
print(cross_tab9)

# Add percentages to the table
cross_tab9_percent <- prop.table(cross_tab9, margin = 2) * 100
print(cross_tab9_percent)

cross_tab10 <- table(df$Income2, df$Groups)
print(cross_tab10)

# Add percentages to the table
cross_tab10_percent <- prop.table(cross_tab10, margin = 2) * 100
print(cross_tab10_percent)

cross_tab11 <- table(df$`Are you trying to lose weight?`, df$Groups)
print(cross_tab11)

# Add percentages to the table
cross_tab11_percent <- prop.table(cross_tab11, margin = 2) * 100
print(cross_tab11_percent)

cross_tab12 <- table(df$Check_Ingredients, df$Groups)
print(cross_tab12)

cross_tab12_percent <- prop.table(cross_tab12, margin = 2) * 100
print(cross_tab12_percent)

#Ranking preferences


summary_ranking1 <- aggregate(`Cereal healthiness1` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

summary_ranking2 <- aggregate(`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_cUa2Sgw1Z4KERE2` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

summary_ranking3 <- aggregate(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_lnH5RoeqxamC6re` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

summary_ranking4 <- aggregate(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_882CtF42zwvUZv0` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

summary_ranking5 <- aggregate(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_dgaZUlSdxdpoDbM` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

summary_ranking6 <- aggregate(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_3r4Nrp3TqC6BOlg` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

summary_ranking7 <- aggregate(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_6DzLXmUBf30NEXA` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

summary_ranking8 <- aggregate(df$`Cereal healthiness8` ~ Groups, data = df, 
                              FUN = function(x) c(Mean = mean(x), SD = sd(x)))

mean(df$`Cereal healthiness1`)

mean(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_cUa2Sgw1Z4KERE2`)

mean(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_lnH5RoeqxamC6re`)

mean(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_882CtF42zwvUZv0`)

mean(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_dgaZUlSdxdpoDbM`)

mean(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_3r4Nrp3TqC6BOlg`)

mean(df$`Rank the 8 cereal packages from most preferred to least preferred by dragging the products to change their order of position. The blue number on the left side indicates the position of the product in the list. - IM_6DzLXmUBf30NEXA`)

mean(df$`Cereal healthiness8`)

cross_tab13 <- table(df$Check_Ingredients, df$Groups)
print(cross_tab12)

cross_tab12_percent <- prop.table(cross_tab12, margin = 2) * 100
print(cross_tab12_percent)




```

